---
title: "Class 11 Structural Bioinformatics"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Section 1. The PDB

Q1. Determine the percentage of structures solved by X-Ray and Electron Microscopy. What proportion of structures are protein?

```{r}
stats <- read.csv("Data Export Summary.csv", row.names = 1)
stats
```
```{r}
(prop.table(stats$Proteins))*100
```


```{r}
stats$Total[1]/sum(stats$Total) * 100
percent.by.method <- stats$Total/sum(stats$Total) * 100
names(percent.by.method) <- rownames(stats)
percent.by.method
```

```{r}
sum(stats$Proteins)/ sum(stats$Total) * 100
```

## How many HIV-1 protease structures are in the current PDB?

##Section 2

##Section 3


## First load the package

```{r}
library(bio3d)
```

```{r}
example(bio3d)
```

## Now we can use the functions from this bio 3d package

```{r}
pdb <- read.pdb("1hsg")
pdb
```

## ~ To find out what something is

```{r}
pdb$atom
```

## aa321 to change 3 letters to 1 letter code for amino acids

```{r}
pdb$atom$resid
```

```{r}
head (aa321( pdb$atom$resid))
```

## Q8. Use the Bio3D write.pdb() function to write out a protein only PDB file for viewing in VMD. Also write out a second separate PDB file for the ligand with residue name MK1. (~ ~)

## We want to select out the protein and drug only parts of these molecular PDB files.

```{r}
prot.inds <- atom.select(pdb, "protein")
prot.inds
```
##(^3 xyz for every atom)

```{r}
prot.pdb <- trim.pdb(pdb, prot.inds)
write.pdb(prot.pdb, file = "protein.pdb")
```

## Let's do the same thing for our drug (these are new funtions! know)

```{r}
lig.inds <- atom.select(pdb, "ligand")
lig.pdb <- trim.pdb(pdb, lig.inds)
write.pdb(lig.pdb, file = "ligand.pdb")
```


## See slides for this..have to install something else and will get VMD plot in R!

```{r}
library(bio3d.view)
view(pdb, "overview")
```





