---
title: "Class 13: Structure based drug discovery"
author: "Susanti Sarkar"
date: "2/19/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Class 13 hands on W/S: Prepare HIV-protease molecule for docking

First get a PDB structure from the online database then clean it up for docking

```{r}
library("bio3d")
```

```{r}
file.name <- get.pdb("1hsg")
```

```{r}
file.name
```


Read file into R and clean it up (remove non- protein bits) and also we will save the ligand into a separate file

```{r}
hiv <- read.pdb(file.name)
hiv
```


## Q1: What is the name of the two non protein resid values in this structure? What does resid correspond to and how would you get a listing of all resid values in this structure? 

Ans: see above (by running hiv)

Non-protein/nucleic resid values: [ HOH (127), MK1 (1) ]

##1.2 Prepare initial protein and ligand input files

This function will not have any non-protein residues!:
```{r}
prot <- trim.pdb(hiv, "protein")
prot
```

To create a new file of this under "Files" tab:(for next one can use 1hsg_ligand)

```{r}
write.pdb(prot, file = "1hsg_protein.pdb")
```

```{r}
lig <- trim.pdb(hiv, "ligand")
lig
```

```{r}
write.pdb(lig, file = "1hsg_ligand.pdb")
```

## 1.3 Using AutoDockTools to setup protein docking input

## 1.5 Prepare a docking configuration file

## 2.3 Inspecting your docking results  (~b/c pdbqt can't be opened in VMD)
used "all.pdbqt" because that was what we called the output ("out") in our config.txt file

```{r}
library(bio3d)
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("ligand.pdbqt")
rmsd(ori, res)
```

## Q6: How would you determine the RMSD for heavy atoms only (i.e. non hydrogen atoms)? 

## Sections 3 and 4?

## Normal mode Analysis

```{r}
pdb <- read.pdb("1HEL")

m <- nma(pdb)
plot(m)
```


```{r}
mktrj(m, mode = 7, file = "nma_7.pdb")
```

#^ load into VMD and run to see flexibility


