---
title: "Class 14: Genome Informatics I"
author: "Susanti Sarkar"
date: "2/21/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Hands-on W/S

Q5: What proportion of the Mexican Ancestry in Los Angeles sample population (MXL) are homozygous for the asthma associated SNP (G|G)? 

Read file from Ensemble

http://uswest.ensembl.org/Homo_sapiens/Variation/Sample?db=core;r=17:39894595-39895595;v=rs8067378;vdb=variation;vf=362656008#373531_tablePanel

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")
head(mxl)
```

```{r}
table(mxl$Genotype..forward.strand.)
```

```{r}
sum(mxl$Genotype..forward.strand. == "G|G")
```

## !!! HOW TO CALC PERCENTAGE!!!

```{r}
table(mxl$Genotype..forward.strand.)/nrow(mxl) * 100
```

Q6. Back on the ENSEMBLE page, search for the particular sample HG00109. This is a male from the GBR population group. What is the genotype for this sample? 
G|G

## Section 2

## RNA-Seq

Fastq quality scores

Q: Does the first sequence have good quality?

```{r}
#install.packages("seqinr")
```

```{r}
#install.packages("gtools")
```

```{r}
q <- "DDDDCDEDCDDDDBBDDDCC@"
library(seqinr)
library(gtools)

asc( s2c(q))
```

## Section 4: Population Scale Analysis 

Does the genotype for rs9067378 influence expression of the important asthma linked genes we found?

```{r}
geno <- read.table("sample geno.txt")
head(geno)
```

```{r}
table(geno$geno)
```

```{r}
inds <- geno$geno == "G/G"
summary(geno$exp[inds])
```

```{r}
inds.aa <- geno$geno == "A/A"
summary(geno$exp[inds.aa])
```

```{r}
inds.ag <- geno$geno == "A/G"
summary(geno$exp[inds.ag])
```

We want some nice figure that shows the distribution of these expression values?

```{r}
boxplot(exp ~ geno, geno)
```

From e.g. rmd file:

```{r}
library(ggplot2)

```










